Trends of SDR in Thessaloniki

### 2023-09-13 Article.Rmd
Commit 2023-09-13 10:10

<!-- \footnotesize -->
```{r trendtable, echo=F}
LT <- data.table(read.csv("./figures/tbl_longterm_trends.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE))
LT <- LT[grep("SDR", LT$var), ]
LT$slope.sd           <- NULL
LT$slope.ConfInt_0.95 <- NULL
LT$slope.ConfInt_0.99 <- NULL
LT$var                <- NULL
setorder(LT, -slope.stat_sig)
rownames(LT) <- NULL
names(LT)    <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Trend statistical signif. [%]")
## no need all are 100%
LT$`Trend statistical signif. [%]` <- NULL
## numeric presision
LT$`Trend [%/year]` <- signif(LT$`Trend [%/year]`, 3)
LT$`Trend p-value`  <- signif(LT$`Trend p-value`,  3)

panderOptions("table.alignment.default", "center")
pander(LT,
       caption = paste0("\\label{tab:trendtable}Trends of daily SDR means, for different sky conditions for ", year(min(ALL_1_daily_DESEAS$Date)), " - ", year(max(ALL_1_daily_DESEAS$Date)), ". For all cases the statistical significance is above $99.9\\%$."))
# knitr::kable(LT, caption = "Trends of daily means by sky conditions.")
## some vars to use later
alltrend   <- signif(LT[`Sky condition` == "All sky cond.",   `Trend [%/year]`], 2)
cleartrend <- signif(LT[`Sky condition` == "Clear sky cond.", `Trend [%/year]`], 2)
cloudtrend <- signif(LT[`Sky condition` == "Cloudy cond.",    `Trend [%/year]`], 2)
```
<!-- \normalsize -->

>>>>

<!-- \footnotesize -->
```{r trendtable, echo=F}
LT <- data.table(read.csv("./figures/tbl_longterm_trends.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE))
LT <- LT[grep("SDR", LT$var), ]
LT$slope.sd           <- NULL
LT$slope.ConfInt_0.95 <- NULL
LT$slope.ConfInt_0.99 <- NULL
LT$var                <- NULL
setorder(LT, -slope.stat_sig)
rownames(LT) <- NULL
names(LT)    <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Trend statistical signif. [%]")
## no need all are 100%
LT$`Trend statistical signif. [%]` <- NULL
## numeric precision
LT$`Trend [%/year]` <- signif(LT$`Trend [%/year]`, 3)
LT$`Trend p-value`  <- signif(LT$`Trend p-value`,  3)

## some vars to use later
alltrend   <- signif(LT[`Sky condition` == "All sky cond.",   `Trend [%/year]`], 2)
cleartrend <- signif(LT[`Sky condition` == "Clear sky cond.", `Trend [%/year]`], 2)
cloudtrend <- signif(LT[`Sky condition` == "Cloudy cond.",    `Trend [%/year]`], 2)

panderOptions("table.alignment.default", "center")
pander(LT,
       caption = paste0("\\label{tab:trendtable}Trends of daily SDR means, for different sky conditions for ", year(min(ALL_1_daily_DESEAS$Date)), " - ", year(max(ALL_1_daily_DESEAS$Date)), ". For all cases the statistical significance is above $99.9\\%$."))
```
<!-- \normalsize -->
